Joint analysis of read count data

### 2020-09-04 combined_analysis/combine_all_data.Rmd
Fix Dx

form = ~ (1|Dx) + Reported_Gender + RIN + ageOfDeath + scale(IntronicRate)*Cohort + scale(IntragenicRate)*Cohort + scale(IntergenicRate)*Cohort + scale(rRNARate)*Cohort + (1|Region:Cohort) + (1|Institution:Cohort) + (1|Region:Cohort) + (1|Individual_ID)

@@

```{r differential.expression.simple}

form = ~ 0 + Dx + Reported_Gender + RIN + ageOfDeath + scale(IntronicRate)*Cohort + scale(IntragenicRate)*Cohort + scale(IntergenicRate)*Cohort + scale(rRNARate)*Cohort + (1|Region:Cohort) + (1|Institution:Cohort) + (1|Region:Cohort) + (1|Individual_ID)

@@

>>>>

form = ~ (1|Dx) + Reported_Gender + RIN + ageOfDeath + scale(IntronicRate)*Cohort + scale(IntragenicRate)*Cohort + scale(IntergenicRate)*Cohort + scale(rRNARate)*Cohort + (1|Institution:Cohort) + (1|Region:Cohort) + (1|Individual_ID)

@@

### Test marginals
```{r differential.expression.simple}

form = ~ 0 + Dx + Reported_Gender + RIN + ageOfDeath + scale(IntronicRate)*Cohort + scale(IntragenicRate)*Cohort + scale(IntergenicRate)*Cohort + scale(rRNARate)*Cohort + (1|Institution:Cohort) + (1|Region:Cohort) + (1|Individual_ID)

@@

```{r plots.marginal}
# Disease
fig1 = plotVolcano( topTable(fit_marginal, "Scz", number=Inf) ) + ggtitle("SCZ")
fig2 = plotVolcano( topTable(fit_marginal, "BP", number=Inf) ) + ggtitle("BP")

cowplot( fig1, fig2, ncol=2)

# Sex
tab = topTable(fit_marginal, "Reported_GenderMale", number=Inf) %>% getGeneSymbol

fig3 = plotVolcano( tab ) + ggtitle("Sex")
fig4 = plotVolcano( tab[tab$Chrom %in% 1:22,] ) + ggtitle("Sex")

cowplot( fig3, fig4, ncol=2)
```

```{r exit, cache=FALSE}
knitr::knit_exit()
```

### Test Diagnosis * Sex
```{r differential.expression.interaction.DxSex}

form = ~ 0 + Dx*Reported_Gender + RIN + ageOfDeath + scale(IntronicRate)*Cohort + scale(IntragenicRate)*Cohort + scale(IntergenicRate)*Cohort + scale(rRNARate)*Cohort + (1|Institution:Cohort) + (1|Region:Cohort) + (1|Individual_ID)

# SCZ by sex
L_SCZ = Lbase
L_SCZ['DxSCZ:Reported_GenderMale'] = 1
L_SCZ['DxControl:Reported_GenderMale'] = -1
L_SCZ['DxSCZ'] = -1
L_SCZ['DxControl'] = 1 
# (A - B) - (C - D) = A - B - C + D

L = cbind(	SczSex = L_SCZ)

fit_interaction_DxSex = dream(vobj, form, METADATA, L=L,BPPARAM = SnowParam(18))
```

### Test Region * Sex
```{r differential.expression.interaction.RegionSex, eval=FALSE}

form = ~ 0 + Dx + Region*Reported_Gender + RIN + ageOfDeath + scale(IntronicRate)*Cohort + scale(IntragenicRate)*Cohort + scale(IntergenicRate)*Cohort + scale(rRNARate)*Cohort + (1|Institution:Cohort) + (1|Cohort) + (1|Individual_ID)

# SCZ by sex
L_SCZ = Lbase
L_SCZ['DxSCZ:Reported_GenderMale'] = 1
L_SCZ['DxControl:Reported_GenderMale'] = -1
L_SCZ['DxSCZ'] = -1
L_SCZ['DxControl'] = 1 
# (A - B) - (C - D) = A - B - C + D

L = cbind(	SczSex = L_SCZ)

fit_interaction_RegionSex = dream(vobj, form, METADATA, L=L,BPPARAM = SnowParam(18))
```

### Test Region * Disease
```{r differential.expression.interaction.RegionDx, eval=FALSE}

form = ~ 0 + Region*Dx + Reported_Gender + RIN + ageOfDeath + scale(IntronicRate)*Cohort + scale(IntragenicRate)*Cohort + scale(IntergenicRate)*Cohort + scale(rRNARate)*Cohort + (1|Institution:Cohort) + (1|Cohort) + (1|Individual_ID)

# SCZ by sex
L_SCZ = Lbase
L_SCZ['DxSCZ:Reported_GenderMale'] = 1
L_SCZ['DxControl:Reported_GenderMale'] = -1
L_SCZ['DxSCZ'] = -1
L_SCZ['DxControl'] = 1 
# (A - B) - (C - D) = A - B - C + D

L = cbind(	SczSex = L_SCZ)

fit_interaction_RegionSex = dream(vobj, form, METADATA, L=L,BPPARAM = SnowParam(18))
```
